% Lab 7 writeup
% written by Walter B. Vaughan

\documentclass[11pt]{article}


\author{Walter B. Vaughan\\
        \small CSC 134 -- Section 200 -- Fall 2014\\
        \small Catawba Valley Community College}
\title{Lab 7}
\date{\vspace{-5ex}}


\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}
\usepackage[margin=.5in]{geometry}
\usepackage{indentfirst}


\lstset{frame=tb,
	language=C++,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=left,
	numberstyle=\color{Gray},
	keywordstyle=\color{BlueViolet},
	commentstyle=\color{Gray},
	stringstyle=\color{OliveGreen},
	breaklines=true,
	breakatwhitespace=true,
	showstringspaces=false,
	tabsize=4
}

\begin{document}

\maketitle


\section*{Pre-Lab Questions}
\begin{enumerate}
    \item The first subscript of every array in C++ is \texttt{0} and the last is \texttt{1} less than the total number of locations in the array.

    \item The amount of memory allocated to an array is based on the \emph{type of data to be stored} and the \emph{number} of locations or size of the array.

    \item Array initialization and processing is usually done inside a \emph{loop}.

    \item The \lstinline{typedef} statement can be used to declare an array type and is often used for multidimensional array declarations so that when passing arrays as parameters, brackets do not have to be used.
    \item Multi-dimensional arrays are usually processed within \emph{nested} loops.

    \item Arrays used as arguments are always passed by \emph{pointer}.


    \item In passing an array as a parameter to a function that processes it, it is often necessary to pass a parameter that holds the \emph{number} of \emph{elements} used in the array.

    \item A string is an array of \lstinline{char}s.

    \item Upon exiting a loop that reads values into an array, the variable used as a \emph{subscript/counter} to the array will contain the size of that array.

    \item An $n$-dimensional array will be processed within $n$ nested loops when accessing all members of the array.
\end{enumerate}
\newpage

\section*{7.1 --- Working with One-Dimensional Arrays}
\begin{description}
    \item[Exercise 2:] The completed program from \textbf{Exercise 1} is attached as \texttt{testscore.ex1.cpp}, and the results of using the input \texttt{90 45 73 62 -99} is as follows: \begin{verbatim}
The average of all the grades is 69.3333

The highest grade is 90

The lowest grade is 45
    \end{verbatim}
    \item[Exercise 3] was completed and the relevant version of the program is attached as \texttt{testscore.ex3.cpp}.
\end{description}

\section*{7.2 --- Strings as Arrays of Characters}
    The program was completed and passed all of the test cases, and it is attached as \texttt{student.cpp}.

\section*{7.3 --- Working with Two-Dimensional Arrays}
\begin{description}
    \item[Exercise 1] was completed and the relevant code is attached as \texttt{price.ex1.cpp}.
    \item[Exercise 2:] \lstinline{getPrices} has its dimension parameters passed by reference because that function actually needs to modify the variables \lstinline{rowsUsed} and \lstinline{colsUsed} for later use in \lstinline{main}. \lstinline{printPrices} only needs to read the values given for the table dimensions.
    \item[Exercise 5:] The changes described in \textbf{Exercises 3 \& 4} were implemented and the resulting program is attached as \texttt{price.ex5.cpp}. The ouput of the program, given the Lab-specified test inputs is as follows: \begin{verbatim}
    1.45    2.56   12.98
   37.86  102.34   67.89
The highest price in the table is 102.34
The lowest price in the table is 1.45
\end{verbatim}
    \item[Exercise 7:] The program was completed as instructed in \textbf{Exercise 6}, is included as \texttt{quartsal.cpp}, and produces the output described, as follows: \begin{verbatim}
      YEAR Quarter 1 Quarter 2 Quarter 3 Quarter 4
      2000        72        80        60       100
      2001        82        90        43        98
      2002        64        78        58        84
\end{verbatim}
\end{description}

\section*{7.4 --- Student Generated Code Assignments}
\begin{description}
    \item[Option 1] is attached as \texttt{7.4.ages.cpp}.
    \item[Option 2] is attached as \texttt{7.4.temperatures.cpp}.
    \item[Option 3] is attached as \texttt{7.4.grades.cpp}. I chose to write the program to use a 5-element array which keeps track of the total number of each grade letter. Writing the program as inferred by the Lab instructions creates a totally unnecessary and arbitrary limit of 50 grades input, and requires that the counts be tallied via 5 separate loops through the array. My solution seems like a much more sane solution to the problem presented.
\end{description}
\end{document}
